DOpElib: Differential Equations and Optimization Environment; A Goal Oriented Software Library for Solving PDEs and Optimization Problems

### 2012-11-23 Paper_May_2012/main.tex
Update der DOpEwebadresse, minor typos.

After the usual preamble, in which we include the necessary header-files from \deal{}, \dope{} and our own problem (i.e. \texttt{localfunctional.h} and \texttt{localpde.h}), we start by defining an instance of a \texttt{ParameterReader}-object, which handles run-time parameter.
\begin{lstlisting}
   ParameterReader pr;
\end{lstlisting}
In a text-file we might specify some problem-related parameters (for instance the viscosity $\nu$), but also general parameters for (non)-linear solvers and the output of computed data. 
After that, we create a triangulation of the domain $\Omega$ named \texttt{triangulation}.

@@

This means for the user only the derivatives of the functional and the PDE 
needs to be provided in addition to the 
\begin{lstlisting} 
  void CellEquation_U(...)
   {
     // implement directional derivative of the CellEquation
   }
\end{lstlisting}
and functional terms, i.e.,     
\begin{lstlisting} 
  virtual void BoundaryValue_U(...)
      {
        // implement here the derivative of 
        // the boundary cost functional
      }
\end{lstlisting}

>>>>

After the usual preamble, in which we include the necessary header-files from \deal{}, \dope{} and our own problem (i.e. \texttt{localfunctional.h} and \texttt{localpde.h}), we start by defining an instance of a \texttt{ParameterReader}-object, which handles run-time parameters.
\begin{lstlisting}
   ParameterReader pr;
\end{lstlisting}
In a text-file we might specify some problem-related parameters (for instance the viscosity $\nu$), but also general parameters for (non)-linear solvers and the output of computed data. 
After that, we create a triangulation of the domain $\Omega$ named \texttt{triangulation}.

@@

This means for the user only the derivatives of the functional and the PDE 
needs to be provided in addition to the 
\begin{lstlisting} 
  void CellEquation_U(...)
   {
     // implement directional derivative of the CellEquation
   }
\end{lstlisting}
and functional terms, i.e.,     
\begin{lstlisting} 
  void BoundaryValue_U(...)
   {
     // implement here the derivative of 
     // the boundary cost functional
   }
\end{lstlisting}
